Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-05 manuscript.Rmd
abstract and intro

title: "Reproducible Research: A Tutorial on how to do the same thing more than once in R"

@@

  Something is called reproducible when independend researcher arrive at the same results from the same data.

@@

  Technological advancements now enable scientists to achieve a much higher standard;
  one in which any individual can be granted access to a digital research repository, and reproduce the analyses from raw data to final manuscript with a single command.

@@

  This paper introduces `repro`; an R-package that guides researchers in the installation and use of the tools required for computational reproducibility.
  It includes a tutorial on how to make a research project reproducible with the aid of `repro`.
  Finally, it introduces novel applications of reproducibility tools for scientific research, notably it includes the preregistration of study plans as reproducible computer code.
  Since computer code describes study plans more precisely than prose, this circumvents the shortcomings of ambiguous preregistrations that give researchers undesired degrees of freedom.
  Reproducibility made convenient with automation has hence a wide range of applications to accelerate scientific progress.

@@

Scientists increasingly strive to make research data, materials, and analysis code openly available i.e. within the Open Science movement.
Sharing these types of digital research products has the potential to increase scientific efficiency by enabling researchers to learn from each other and reuse materials, and to increase scientific reliability by facilitating the review and replication of published research results.
To some extent these potential benefits are contingent on whether these digital research products are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research results hingeson their objectivity.
Objectivity in this context means "in principle it [the research finding] can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper].
Only something reproducible can be tested and understood by anyone.
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project with all code, data, and materials reproducible comes with a variety of challenges (multiple versions of code and data, copy-and-paste errors, missing software, ambiguous computation), and there is a dire need for reproducibility standards.
With the technological advancement, it is now possible to make all digital products related to a research project available so that a research project can be reproduced with minimal effort.

This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project and are willing to make relevant code, data, and materials available, whether publicly or on request.
We pursue two aims.

First, we introduce the reader to a workflow that maximizes the potential reproducibility of a research project.

This workflow builds on several technical solutions originating in the software engineering community. 
We discuss how these solutions address four common threats to reproducibility [see @Peikert2019 for details] and how they form a coherent workflow.
We further demonstrate how the R package `repro` supports researchers in adopting this workflow.
Second, we discuss opportunities that the reproducible workflow affords to improve not only how research outputs are created and recreated, but also how research itself is conducted.
One such opportunity is a strictly reproducible and unambiguous form of preregistration [@NosekRevolution2018] that builds upon an implementation of this reproducible workflow, the so-called *preregistration as code* (PAC).
PAC involves preregistering the intended analysis code and the bulk of the manuscript as a dynamic document, including the Introduction, Methods, and Results sections.
The resulting dynamic document closely resembles the final manuscript, but temporarily uses simulated data to generate placeholder results (e.g. figures, tables and statistics).
Once the empirical data are analyzed, the Results are updated automatically, and the Discussion can be written.

@@

This tutorial therefore demonstrates how to make R-based research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood that a project will remain reproducible as long as possible.
An easy-to-use standard, on the other hand, is more likely to be adopted.
Our approach is to promote broad adoption of easy-to-use practices, i.e., a "low threshold", and ensure that these practices are compatible with more complex rigorous solutions, i.e., a "high ceiling".
As researchers become more proficient with the tools involved, they can thus improve the reproducibility of their work.
The first part of this tutorial outlines threats to reproducibility and how the here presented reproducibility standard addresses these threats.

>>>>

title: "Reproducible Research in R: A tutorial on how to do the same thing more than once"

@@

  Something is called reproducible when an independent person obtains the same results from the same data.

@@

  Technological advancements now enable scientists to achieve a more comprehensive standard;
  one in which any individual can be granted access to a digital research repository, and reproduce the analyses from the raw data to the final report including all relevant statistical analyses with a single command.

@@

  This paper introduces `repro`, an R-package, which guides researchers in the installation and use of the tools required for making a research project reproducible.
  Finally, we suggest the use of the proposed tools for the preregistration of study plans as reproducible computer code (preregistration as code; PAC).
  Since computer code represents the planned analyses exactly as they will be executed, it is more precise than natural language descriptions of those analyses, which merely complement the PAC as a more readable summary. 
  PAC circumvents the shortcomings of ambiguous preregistrations that may give researchers undesired degrees of freedom.
  <Hence, reproducibility made convenient with automation has a wide range of applications to accelerate scientific progress.

@@

Scientists increasingly strive to make research data, materials, and analysis code openly available <!-- AB "i.e." does not work in this context. I just removed this because it's irrelevant whether this happens within the movement or not?!-->
Sharing these types of digital research products has the potential to increase scientific efficiency by enabling researchers to learn from each other and reuse materials, and to increase scientific reliability by facilitating the review and replication of published research results.
To some extent these potential benefits are contingent on whether these digital research products are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research results hinges on their objectivity.
Objectivity in this context means "in principle it [the research finding] can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper].
Only something reproducible can be tested and understood by anyone.
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project with all code, data, and materials reproducible comes with a variety of challenges (e.g., missing software or ambiguous documentation of all steps taken <!-- AB the previous list was difficult to understand without more context; these two points are hopefully better to understand--> ), and there is a dire need for reproducibility standards.
With the technological advancement, it is now possible to make all digital products related to a research project available so that a research project can be reproduced with minimal effort.

This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project and are willing to make relevant code, data, and materials available, whether publicly or on request.
We pursue two aims. First, we introduce the reader to a workflow that maximizes the potential reproducibility of a research project. Second, we introduce a computational preregistration scheme based on reproducible research projects.
<!-- AB Absätze können nicht nur einen Satz haben! Außerdem fehlte das "Second"-->

<!--AB "This" geht nicht am Absatzanfang--> The proposed workflow builds on several technical solutions originating from software engineering. 
We discuss how these solutions address four common threats to reproducibility [see @Peikert2019 for details] and how they interact to form a coherent workflow.
We further demonstrate how the R package `repro` supports researchers in adopting this workflow.
Second, we discuss opportunities that the reproducible workflow affords to improve not only how research outputs are created and recreated, but also how research itself is conducted.
One such opportunity is a strictly reproducible and unambiguous form of preregistration [@NosekRevolution2018] that builds upon an implementation of this reproducible workflow, the so-called *preregistration as code* (PAC).
PAC involves preregistering the intended analysis code and the bulk of the manuscript as a dynamic document, including typical sections like Introduction, Methods, and Results.
The resulting dynamic document closely resembles the final manuscript, but temporarily uses simulated data to generate placeholder results (e.g. figures, tables and statistics).
With these placeholders, authors preregister the exact presentation of their results without having seen real data yet.
Once the empirical data are analyzed, the Results are then updated automatically, and the Discussion can be written to finalize the report.

@@

Therefore, this tutorial demonstrates how to make R-based research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood that a project will remain reproducible as long as possible.
An easy-to-use standard, on the other hand, is more likely to be adopted.
Our approach is to promote broad adoption of easy-to-use practices, i.e., a "low threshold", and ensure that these practices are compatible with more complex rigorous solutions, i.e., a "high ceiling".
As researchers become more proficient with the tools involved, they can thus improve the reproducibility of their work.
<!--The first part... dieser Satz wirkte verloren. Habe ich gestrichen-->
